Title

### 2013-01-31 main.tex
continuing to move \section directives into subimported files
remove stray unicode characters from bibliography files
tracking down some more unicode
added plasmon file, include cc warning on pole piece figure
expand on plasmon
remove some unicode
use space between word and \cite
added some more section stubs
removed old semiconductor section and add apl paper as este
add apl bibliography up to entry 13
added \inputdata function and inputdata boolean to include larger datasets or not (for speed)
redo some headings in plasmon section
created separate abbreviations file to keep main cleaner. add

\usepackage{graphicx}
\graphicspath{{./images/}}
\DeclareGraphicsExtensions{.png,.pdf,.jpg}
\input{mytikz}

@@

@@

\ifthenelse{\boolean{usebiblatex}}{
  \usepackage{biblatex}
  \addbibresource{bibliography.bib}
}{}
%% ==

@@

\listofabbreviations
\begin{list}
  {}
  {\setlength{\labelwidth}{1in}
   \setlength{\leftmargin}{1.5in}
   \setlength{\labelsep}{.5in}
   \setlength{\rightmargin}{\leftmargin}}

  \abbr{AG}{Analytic Gaussian (Model)}
  \abbr{AR}{Anti-Reflection}
  \abbr{DC}{Direct Current (i.e. Static Electric Field)}
  \abbr{DTEM}{Dynamic Transmission Electron Microscopy}
  \abbr{FWHM}{Full-Width Half Maximum}
  \abbr{GRIN}{Gradient Index (of Refraction)}
  \abbr{GVD}{Group Velocity Dispersion}
  \abbr{HW1/eM}{Half-Width 1/e Maximum}
  \abbr{LHS}{Left Hand Side}
  \abbr{ML}{Mode-Locked}
  \abbr{Q}{Quality Factor}
  \abbr{RHS}{Right Hand Side}
  \abbr{RF}{Radio Frequency}
  \abbr{SBR}{Saturable Bragg Reflector}
  \abbr{TLS}{Thermal Lens Shaping}
  \abbr{TEM$_{00}$}{Tranvserse ElectroMagnetic 00 Mode}
  \abbr{TM$_{010}$}{Tranvserse Magnetic 010 Mode}
  \abbr{UED}{Ultrafast Electron Diffraction}
  \abbr{UEM}{Ultrafast Electron Microscope}
  \abbr{UIC}{University of Illinois at Chicago}
\end{list}

@@

  \subimport{inc/liouvilles_theorem/}{liouvilles_theorem}

  \subimport{inc/initial_conditions/}{initial_conditions}

  \subimport{inc/external_forces/}{external_forces}

@@

@@

\section{Chamber Design}

\section{Accelerator Design}

\section{Magnetic Lenses}

@@

\section{Deflection Plates}

@@

@@

\section{Nanopatterned (Plasmonic) Photocathodes}

\section{Semiconductor Photocathodes}

  \subimport{inc/semicond/}{semicond}

@@

%\appendices
%\appendix
%\newpage

%% Special handling for using biblatex vs bibtex ==
\ifthenelse{\boolean{usebiblatex}}{
  \printbibliography
}{
  \bibformc
  \bibliography{bibliography,biblaser}
}
%% ==

>>>>

\usepackage{graphicx}
\graphicspath{{./images/}}
\DeclareGraphicsExtensions{.png,.pdf,.jpg}
\input{mytikz}
\setboolean{inputdata}{true}
\usepackage{fancyvrb}
\input{pygments}

@@

\usepackage{color}
\providecommand{\fixme}[1]{\textcolor{red}{#1}}

@@

\ifthenelse{\boolean{usebiblatex}}{
  \usepackage{biblatex}
  %\usepackage[backend=biber]{biblatex-chicago}
  \addbibresource{bibliography.bib}
  \addbibresource{biblaser.bib}
  \addbibresource{bibeste.bib}
}{}
%% ==

@@

\input{abbreviations}

@@

  \subimport{inc/extension/initial_conditions/}{initial_conditions}

  \subimport{inc/extension/liouvilles_theorem/}{liouvilles_theorem}

\section{Free Expansion Results}

\subsection{Comparison to Other Articles}

\subsection{Trends for Initial Shapes}

  \subimport{inc/extension/external_forces/}{external_forces}

  \subimport{inc/gun/}{gun_model}

  \subimport{inc/extension/implementation/}{implementation}

@@

  \begin{figure}
    \centering
    \includegraphics{inc/hardware/column.jpg}
    \caption{
      Image of the majority of the prototype UEM column at UIC.
      The main vacuum chamber is laid sideways, with the high voltage (gun) at the left and the imaging system on the right.
      The magnetic levitated turbo pump hangs below the column, a scroll pump used for backing is not pictured.
      The laser system is in the background.
      All of the above is mounted on a custom shaped active vibration-canceling optical table.
      The electronic control systems are not pictured.
    }
    \label{fig:column-pic}
  \end{figure}

@@

  \subimport{inc/hardware/}{column}

  \subimport{inc/gun/}{gun_design}

@@

  \subimport{inc/hardware/}{deflector}

@@

  \subimport{inc/photocathode/setup/}{setup}

@@

  \subimport{inc/photocathode/plasmon/}{plasmon}

  \subimport{inc/photocathode/este/}{este}

@@

%uncomment when multiple appedicies are used 
%\appendices
\appendix
  \subimport{inc/extension/implementation/}{appendix-script}

\newpage

%% Special handling for using biblatex vs bibtex ==
\ifthenelse{\boolean{usebiblatex}}{
  \printbibliography
}{
  \bibformc
  \bibliography{bibliography,biblaser,bibeste}
}
%% ==
